Adopting agile in the large: motivations, success factors and challenges

### 2014-05-13 journal/article.tex
Work in progress: External QA

Some cases reported  Some organizations used a quality assurance group separate
from development.

@@

@@

>>>>

@@

% When developing large software systems individual teams will not have resources
% to verify on their own that the results of an iteration pass the QA of the
% entire system. In these cases separate testing groups will perform heavy testing
% tasks.
%  
% The activities of specialized QA teams still needs to be coordinated with
% development teams

In an enterprise setting quality assurance (QA) tasks will require effort beyond
the general agile convention of doing testing within a crossfunctional team. In
large development efforts the agile model may need to be extended to accomodate
additional testing [P31]. Organizations may have existing separate QA teams that
must be coordinated to work with development teams [P17, P30, P48]. Integrating
enterprise scale QA will pose some additional challenges to agile methods.

Full quality assurance of a system requires special testing such as performance,
load, and memory testing, but agile methods lacks focus on them [P17]. These
testing activities can not be done within boundaries of user stories, and
require more resources than teams can spare [P31]. As testing tasks overlap team
boundaries it is sensible having a separate teams for the tasks, but
coordination practice between specialized QA teams and development teams needs
to be defined [P28, P48].

Some cases reported on problems with lack of automated testing. For a large
system the lack of automated tests caused excess testing work and late discovery
of defects [P10, P11, P17].

Still one challenge in QA was the relationship to requirements engineering. The
QA functions were struggling if there was problems such as ambiguity or
ineffective breakdown of large requirements [P48]. In a waterfall model an
extended time was reserved for QA at the end of projects, which allowed to
retroactively resolve ambiguities in requirements [P5]. However, as agile
required QA work to be done incrementally with development problems with
ambiguity in requirements became an impediment to QA [P5].

@@

* There is a separate test team --> Not integrated with development teams
* Problem: There is a 2 iteration lag for defects found by the test team
[P30]

* Separate Systems Teams --> System validation
* Development teams did not know how to create increments that would be testable
* Connection to requirements engineering
[P48]

* There was offshore QA resources --> They still needed to be leveraged
* An arrangement was set up to leverage external QA
[P17]

* Separate QA groups --> General impediment (not elaborated)
[P3] (Skip this? too vague)

ENTERPRISE TESTING EXPLAINED

* Enterprise testing --> Falls outside Scrum
[P31]

* In waterfall there are several test environments the release goes through
* In agile it is hard to fit going through these environments
* Hard to fit large scale testing in agile
* The test environment model had to be revised
[P29]

% LACK OF AUTOMATION
% 
% * Testers were not engaged with the agile process --> For what reason? --> Generally
% [P10]
% * Solution: QA responses are handled in the second half of the sprint
% [P10] (skip this?)
% * There was a separate QA --> It was a bit difficult to integrate QA with the development teams
% * QA tasks did not fit inside sprints --> There was lots of legacy code that needed to be regression tested
% * Legacy code took long to test
% [P10]
% 
% * Lack of automated tests --> Rush in testing
% * Rushing to release --> Little time to test --> Automated tests skipped
% [P11]
% 
% * Continuous build environment missing --> late discovery of bugs
% * Late discovery of bugs --> hard to stay releasable
% * There are iterations that are forced to be only testing and fixing
% * Invest in test automation
% [P17]

% CONNECTION TO RE
% 
% * Separate Systems Teams --> System validation
% * Development teams did not know how to create increments that would be testable
% * Connection to requirements engineering
% [P48]
% 
% * Requirements ambiguity --> Was originally resolved in an extensive QA period in the end of the development cycle
% * QA was struggling --> Requirements were done badly --> Learning was needed  
% [P5]

% SPECIALIZED TESTING
% 
% * Some testing activities are not focused in agile --> Performance, load, memory
% * These testing activities must not be forgotten
% * A separate Integration Test Team --> Works also on these special testing activities
% [P17]
% 
% * Performance, scalability testing --> Require a lot of resources
% * This enterprise testing must be performed --> Teams can not do it
% * These testing types need to be centralized --> Specialized environments, specialized tasks
% * Development teams share the enterprise testing team
% * Solution: A separate EQC was established offsite
% [P31]
% 
% * External system testing team --> Their work is not needed all the time by teams
% * They perform work that is necessary for DoD of teams
% * Problem: How to organize system testing resources so that all teams can be served
% [P28]

("C: QA is difficult in agile" | "C: Problems with separate non-agile QA")

* Separate QA groups --> General impediment (not elaborated)
[P3]
the Amazon PMO may some day become interested in Scrum, but they are enmeshed in
maintaining and thriving within a traditional waterfall paradigm. Another
example is the existence of separate QA groups. Executive sponsorship would help
to begin to break down these entrenched impediments.

* Requirements ambiguity --> Was originally resolved in an extensive QA period in the end of the development cycle
* QA was struggling --> Requirements were done badly --> Learning was needed  
[P5]
There was constant debate over both the meaning of the requirement and whether
or not the requirement was met.  Quality Assurance engineers were frustrated
trying to determine whether or not we should accept this feature.  Simply put,
we had not invested enough of our velocity in either up front or ongoing
requirements elaboration.
Going into the second release, we knew we had to do a better job with managing,
elaborating, and prioritizing requirements.  This had strictly been an issue
regarding where we chose to invest our energy.
Properly managing requirements was critical.

* Testers were not engaged with the agile process --> For what reason? --> Generally
[P10]
INTEGRATING  QA: We noticed that many testing actions were inevitably deferred
until the end of the sprint or remained incomplete, and that the testers seemed
less engaged with the process.
Comment: This does not say that the testers are separate from the team...

* Solution: QA responses are handled in the second half of the sprint
[P10] (skip this?)
How could we adapt Scrum – or otherwise change our own behaviors – in order to
integrate QA, manage dependencies, focus our daily meetings and release software
at the end of sprints of a reasonable duration? Inspired by ideas encountered at
an industry conference (SD Best Practices), the team decided to extend its scrum
approach in two simple ways.
Four weeks still felt like the shortest sprint duration that made sense if our
aim was to deliver potentially shippable releases at the end of each sprint. 
However, the addition of two-week TASK CYCLES [1] provided a way to structure
our time within a sprint to good effect (as shown in Figure 5).  During the
first task-cycle within a sprint the developers would focus on implementation of
backlog items that we expected to appear in the sprint release.  These changes
would be checked into our MAIN  code branch. During the second task cycle within
the sprint the developers would divide their time between resolving issues
reported by QA while testing those backlog items (as a priority), and continuing
to work on backlog items that we expected to appear in the following sprint
release.

* There was a separate QA --> It was a bit difficult to integrate QA with the development teams
* QA tasks did not fit inside sprints --> There was lots of legacy code that needed to be regression tested
* Legacy code took long to test
[P10]
Indeed, each step forward was accompanied by the discovery of additional
challenges (the next layer  of the  onion).  Several new problems now came to
the fore:
(1) REGRESSION DEFECIT: despite tighter integration of the  QA  team,  it
quickly became clear that our large legacy code base made necessary a  much
larger amount of testing than  we  could  easily accommodate  within a sprint,
or even a multisprint release, even when  developers  dropped everything to join
the testing effort  as  a  release approached.

* Lack of automated tests --> Rush in testing
* Rushing to release --> Little time to test --> Automated tests skipped
[P11]
Scrum preaches test driven design and releasable product every two to four
weeks.  For some of our newer products that had been rushed to market, there
were few tests and, due to restructuring, no test teams.  Fortunately, engineers
were used to testing each others’ code within the team.  But there were no
automated builds, and no automated tests, and some test cycles took an entire
week or more.  Since multiple teams were in the same situation, it was easier to
get buy in to launch a Scrum project focused on creating an organization-wide
structure for automating builds and testing that all Cloud Engineering teams
could use.

* There was offshore QA resources --> They still needed to be leveraged
* An arrangement was set up to leverage external QA
[P17]
BMC needed to continue leveraging QA resources in India while adopting agile
methodologies. Their solution was to create blended QA teams that matched one
Lead QA engineer co-located with the US-based development organization with
several QA engineers located in India. The co-located Lead QA engineer provides
the necessary coordination and communication at daily US stand-ups, and then
communicates back to the India-based QA resources on progress and priorities.
The result is that BMC is able to gain the benefits of a round-the-clock QA
cycle.

* Continuous build environment missing --> late discovery of bugs
* Late discovery of bugs --> hard to stay releasable
* There are iterations that are forced to be only testing and fixing
* Invest in test automation
[P17]
One of the most difficult challenges is staying releasable throughout the
development cycle. There are several causes – including late defect discovery
and the deferral of major bugs due in part to lack of a continuous build
environment. In turn, these issues cause the need for multiple hardening
iterations spent on pure test and fix activities. Going forward, BMC will
address these issues with two initiatives:
1. Maintaining and improving the continuous integration environment.
2. A focus on pulling testing forward in the cycle using test-driven development
   (TDD) practices at both the unit test and acceptance test levels, and
   increasing the investment in test automation.

* Some testing activities are not focused in agile --> Performance, load, memory
* These testing activities must not be forgotten
* A separate Integration Test Team --> Works also on these special testing activities
[P17]
It is easy to overlook standard engineering best practices when focusing on the
new planning, development and testing behaviors of the agile paradigm. Sometimes
standard BMC practices like performance testing, load testing and monitory
memory usage weren’t executed until late in the development cycle. Pulling these
activities forward in the release cycle and maintaining an integration test bed
is the responsibility of a newly-formed Integration Test Team that insures that
cross-team functionality is performing properly throughout the release cycle.

* External system testing team --> Their work is not needed all the time by teams
* They perform work that is necessary for DoD of teams
* Problem: How to organize system testing resources so that all teams can be served
[P28]
Both the System Testing team and the Product Metrics team have implemented OH.
Both of these teams perform work that is vital to the Technology team’s
definition of “done” for a sprint; therefore, it is important that scrum teams
have access to these resources. However, not all scrum teams need a dedicated
system testing engineer, and no scrum teams need a dedicated product metrics
analyst. Therefore, these two functional teams are ideal candidates for OH.

The System Testing team has implemented OH for scrum teams to utilize the
expertise of the system testing engineers as well as the system testing
environments. Like the DS team, the System Testing team does not have enough
staff to meet the demands for its services. In addition, many of the tasks that
the system testing engineers do can be performed by other scrum team members.
Therefore, the System Testing team has instituted OH similar to the UE OH.
During the System Testing OH, system testing engineers work with scrum team
members on:

• Training scrum team members on how to use system testing environments and
  tools.
• Reviewing system testing results.
• Validating features that have system testing requirements for scrum teams
  without an assigned system testing engineer.

The Product Metrics team has implemented OH in a similar way. During Product
Metrics OH, the product metrics analysts help scrum team members with:

• Defining what types of metrics are relevant to track the adoption of their features.
• Using and interpreting the feature adoption metrics that are in the metrics database.

* In waterfall there are several test environments the release goes through
* In agile it is hard to fit going through these environments
* Hard to fit large scale testing in agile
* The test environment model had to be revised
[P29]
In a waterfall process, code is iterated and each build is deployed to a
development unit test (DUT) environment.  This environment is primarily used by
developers to test their own code.
When the code has been determined as stabilized, a build is deployed into
another environment called the development integration test (DIT) environment. 
This is the environment where component testing often begins with build
verification and unit tests being run.
When a build it deemed “ready” it is iterated and deployed into a system
integration test environment (SIT) where end-to-end and system testing such as
performance is done.
The last stop for a build is the user acceptance test environment (UAT) where
user and other types of testing is done.
Every major build from release candidates to the final build will eventually
have gone through each environment.  This model while effective in a waterfall
method does not adapt easily to the Scrum Model.

* There is a separate test team --> Not integrated with development teams
* Problem: There is a 2 iteration lag for defects found by the test team
[P30]
The software testing team tried many ways to coordinate with development teams
over the first few sprints, but ultimately decided to run its own Scrum. They
received work items from development teams when work items were “completed.” The
result: a two-week iteration lag between the discovery of a defect and the time
it could be fixed. Defects were queued to enter the development team’s next
sprint. Another iteration lapsed before verification of the fix could occur.
Because of the high cost of fixing defects, triage on defects was conducted by
product owners and testers who chose not to fix some defects in exchange for new
features.

* Enterprise testing --> Falls outside Scrum
[P31]
we discovered some areas that would require us to adapt our chosen Scrum
methodology to account for the realities of complex, large-scale development. 
Two key activities fell outside the scope of our original Scrum framework
1. Informing how things get into the backlog, and 2. Enterprise testing.

* Performance, scalability testing --> Require a lot of resources
* This enterprise testing must be performed --> Teams can not do it
* These testing types need to be centralized --> Specialized environments, specialized tasks
* Development teams share the enterprise testing team
* Solution: A separate EQC was established offsite
[P31]
we realized that we were relying on our partnership with a very large customer
to test the scalability of one of our products.  We would “drop” new code into
their environment after each sprint, and they would let us know where we had
issues. We knew that as we scaled Agile practices to more of the organization,
using our teams and customers as test labs would lead to serious problems. So we
decided to establish a formalized enterprise testing process. According to Scrum
practices, all testing, including enterprise testing, should be done within the
Scrum team, and a user story is only complete once it is fully tested. Certain
types of enterprise testing pose challenges to this principle. Performance
requirements, for instance, are often based on scenarios that transcend
individual user stories. To incorporate performance, scalability and integration
testing, we would have to adapt our Scrum practices.

A few years ago, Borland established an Enterprise Quality Center (EQC) in
Singapore.  This test lab is our central resource for all scalability,
performance and integration testing.

While our solution involves teams being dependent on an external organization
and requires us to have two versions of “complete” for a user story, the benefit
is that the EQC has become a virtual resource that we are able to provision as
needed to the various Scrum teams. While this may be a controversial move, it is
absolutely necessary.  We simply cannot release products that have not been
fully enterprise tested.

* Separate Systems Teams --> System validation
* Development teams did not know how to create increments that would be testable
* Connection to requirements engineering
[P48]
• We agreed to make the Systems Teams (system validation and trials) the
pacemaker – the metronome - of the new agile framework, and it turned out that
moving to time-boxed and phased execution of their activities was actually a
welcome change for many. Instead of random delivery of products to the test and
trial phases, the model these groups developed had a schedule of acceptance
dates, which provided the Systems Teams much more flexibility. It also gave the
teams opportunities for early exposure of defects and integration problems.

• Unfortunately, the Product Teams were not able to deliver software components
that could be tested or trialed early. So in effect, Systems Teams were “all
dressed up with no place to go…”. It seems that the Scrum teams didn’t know how
to break down their work into consumable pieces that could logically be
delivered, tested and trialed incrementally.  Primarily this was because our
portfolio and roadmap processes were at “too high a level”.
